TSELM: Target speaker extraction using discrete tokens and language models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\section{Conclusion}
In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction. Experiments have 
shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
speaker similarity. However, we still have a gap between continuous methods especially in speech intelligibility.

>>>>

\section{Conclusion}
In this work, we introduced a novel way using discrete tokens and language models for target speaker extraction.
We use multiple hidden layers of WavLM and Kmeans tokenizers as encoder, cross attention and language model as our separation model, and a scalable HiFi-GAN to reconstruct the 
audio. 
Experiments have 
shown that our model can achieve excellent performance in terms of speech quality, and comparable performance in terms of speech intelligibility and 
speaker similarity. However, we still have a gap between continuous methods especially in speech intelligibility and speaker similarity. Future research should focus on shrinking 
this gap.
